Sparse Function-space Representation \\ of Neural Networks

### 2023-05-24 paper/main.tex
update app. a

\section{Method details}
\label{app:method}
%
As shown in \cref{eq:dual_param} in the main paper, our method rely on computation of the dual parameters. We show here how we can derive them in general for the family of exponential likelihoods. By rewriting the loss in the natural form, we have,
\begin{equation}
 \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f \rangle
\end{equation}
where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics, and $f$ denotes the neural network output before the link function. 
%given the loss functions we use $t(y) = y$. 
Then, taking the first and second derivatives of the loss in this form become:
\begin{equation}\label{eq:dual_param_app}
  \nabla_{f} - \log p(y_i \mid f) |_{f=f_i} =  - A'(f_i) y_i
  \quad \text{and} \quad
  \nabla^2_{f\!f} - \log p(y_i \mid f) |_{f=f_i} = A''(f_i).
\end{equation}
\todo{check the signs with the main paper}
% The second derivative of the log partition function is easily calculated and
In this section, we provide the derivatives needed for the losses used in this work, \ie, the Gaussian likelihood, used for the regression tasks, the Bernoulli likelihood, for binary classification, and the categorical likelihood, used for multi-class classification.

For regression, the negative log likelihood comes from the Gaussian likelihood, and for a single input it can be written as:
\begin{equation}
	\ell(h(f_i), y_i) = % -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
\end{equation}
where the inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$. Thus, the first and second derivatives are
\begin{equation}
	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} = y_i - f_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1
\end{equation}

>>>>

\section{Method details}
\label{app:method}
%
As shown in \cref{eq:dual_param} in the main paper, our method rely on computation of the dual parameters. We show here how we can derive them in general for the family of exponential likelihoods. By rewriting the loss in the natural form, we have,
\begin{equation}
 \ell(h(f), y) = -\log p(y \mid f) =  A(f)  - \langle t(y), f \rangle
\end{equation}
where $A(f)$ is the log partition function, $h(\cdot)$ is the inverse link function, $t(y)$ are the sufficient statistics, and $f$ denotes the neural network output before the link function. 
%given the loss functions we use $t(y) = y$. 
Then, taking the first and second derivatives of the loss in this form become:
\begin{equation}\label{eq:dual_param_app}
  \nabla_{f} - \log p(y_i \mid f) |_{f=f_i} =  - A'(f_i) y_i
  \quad \text{and} \quad
  \nabla^2_{f\!f} - \log p(y_i \mid f) |_{f=f_i} = A''(f_i).
\end{equation}
\todo{check the signs with the main paper}
% The second derivative of the log partition function is easily calculated and
In this section, we provide the derivatives needed for the losses used in this work, \ie, the mean squared error (MSE) likelihood, used for the regression tasks, the Bernoulli likelihood, for binary classification, and the categorical likelihood, used for multi-class classification.

For regression, the negative log likelihood comes from the MSE, and for a single input it can be written as:
\begin{equation}
	\ell(h(f), y) = \frac{1}{2} (y -f).% -\log \Norm( h(f) | y, \sigma^2) 	= - \log 
\end{equation}
where the inverse link function is simply $h(f) = f$. Thus, the first and second derivatives are
\begin{equation}
	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} = y_i - f_i \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = 1
\end{equation}

In binary classification, we deal with Bernoulli likelihoods. The inverse link function is the sigmoid function $h(f) = \sigma(f) = \frac{1}{1 + e^{-f}}$, and we can then write the negative log likelihood as
\begin{equation}
\begin{aligned}
	\ell(h(f), y) 
	&= -\log \left( \sigma(f)^y (1 - \sigma(f))^{1-y} \right) \\
	&= - y \log(\sigma(f)) - (1-y) \log(1- \sigma(f)) \\
	&= - y f + \log(1 + e^f) 
\end{aligned}
\end{equation}
Then, it follows that the the derivative we are interested in are
\begin{equation}
	\nabla_f \ell(\sigma(f), y_i)|_{f=f_i} = - y_i + \sigma(f_i) \quad \text{ and } \quad  \nabla_{f\!f} \ell(h(f), y_i)|_{f=f_i} = \sigma(f_i) (1 - \sigma(f_i)).
\end{equation}

Moving to the multi class classification, the function outputs is no more a scalar but a vector of logits $\bm{f} \in \R^C$. The inverse link function for the categorical loss is the softmax function $\textrm{Softmax}(\bm{f}) : \R^C \to \R^C$ defined as $h(\bm{f}) = \textrm{Softmax}(\bm{f}) = \frac{\exp(\bm{f})}{ \sum^C_{j=1} \exp(\bm{f}_j)} \in \R^C$. If we write the targets $y_i$ as a one-hot $C$-shaped one-hot encoding vector, we can write the negative log likelihood as:
\begin{equation}
\begin{aligned}
	\ell(h(\bm{f}),\vy) &= - \log\left( \vy^\T \textrm{Softmax}(\bm{f})\right)\\
	&= - y_i \log \left( \left[ \textrm{Softmax}(\bm{f}) \right]_i \right)
\end{aligned}
\end{equation}
where $\left[\textrm{Softmax}(\bm{f})\right]_i = \frac{\exp(\bm{f}_i)}{\sum_{j=1}^{C} \exp(\bm{f}_j)}$ defines the $i$\textsuperscript{th} entry of the logits fed through the $\textrm{Softmax}(\cdot)$ function.
